A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-23 sections/appendix/descrete_event_simulation/main.tex
Change code based on ambulance_game v0.0.2

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean([
    ...     np.mean(w.waiting_times) for w in all_simulations
    ... ])
    >>> mean_wait
    0.35585979549204577

@@

To get the average proportion of individuals within target, run the following
code:

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> (
    ...     overall_proportion,
    ...     class_1_proportion,
    ...     class_2_proportion,
    ... ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ...     runtime=2000,
    ...     target=1,
    ... )
    >>> np.mean(overall_proportion)
    0.45785790578122043

    >>> np.mean(class_1_proportion)
    0.4406768928300989

    >>> np.mean(class_2_proportion)
    0.4840634188366037

>>>>

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ...     target=1,
    ... )
    >>> mean_wait = np.mean([
    ...     np.mean(w.waiting_times) for w in all_simulations
    ... ])
    >>> mean_wait
    0.35585979549204577

@@

    >>> np.mean([p.proportion_within_target for p in all_simulations])
    0.45785790578122043
